---
title: "Content for @WeAreRLadies Rotating Curator"
subtitle: "With {xaringan} and {flipbookr}"
author: "Shannon Pileggi w/ CSS by Silvia Canelón"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{css, echo = FALSE}
/* 
# rem is a relevant font size unit, it stands for "relative to the 'root' em-dash", and it's 16px by default on (all?) HTML pages.

# em is another relevant font size unit, it's relative to the em-dash, and it's relative to the container it's in.

# resource: https://css-tricks.com/rems-ems/
*/

/*-- CODE TEXT  --------*/
/*-- Code chunk --*/
/*
# 1rem or 1em = 16px, it seems !important is necessary here
*/
pre code {
  font-size:          18px !important; 
}


/*-- Line highlighting within code chunk --*/
.remark-code-line-highlighted {
  background-color:   rgba(204, 189, 204, 0.6);
}


/*-- Inline code --*/
/* 
# 1rem = 16px, 1em = 20px, em here means it depends on the size of .remark-slide-content (below). For example, using 0.8em or 80% instead would make the text 80% as large as the .remark-slide-content text size (1.5em below) 
*/

.remark-code, .remark-inline-code {
  font-family: 'Inconsolata', 'Lucida Console', Monaco, monospace; 
  font-size:          1em;
  color: #88398A;
}


/*-- PROSE TEXT --------*/
body { font-family: 'Lato', 'Palatino Linotype', 'Book Antiqua', Palatino, 'Microsoft YaHei', 'Songti SC', serif;}

/*
# 1rem or 1em = 16px, controls size of prose text but not headings
*/

.remark-slide-content {
  font-size:          1.5em; 
}

/*-- Headings --*/
h1, h2, h3 {
  font-family: 'Yanone Kaffeesatz'; 
  font-weight: normal;
  color: #562457;
}

/*-- Links/anchors --*/
a, a > code {
  color: #88398A;
}

/*-- Inverse/divider slides --*/
.inverse {
  background-color: #562457;
}
.inverse, .inverse h1, .inverse h2, .inverse h3, .inverse a, inverse a > code {
  color: #fff;
}

```


```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
#library(extrafont)
library(flipbookr)
library(xaringan)
knitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = " ", cache = F, dpi = 300)
```


---
class: inverse, middle, center


# 1. Walrus operator

---

`r chunk_reveal("walrus", title = "## Walrus operator")`

```{r walrus, include = FALSE}
library(tidyverse)
library(rlang)
library(glue)

suffix <- "A" 

dat <- tibble(x = 1:5) %>%
  mutate(
    "x_{suffix}" := x
  ) 

dat %>% 
  dplyr::select(
    glue::glue("x_{suffix}")
    ) 
```

---
class: inverse, middle, center

# 2. mutate_at + vars + matches


---

`r chunk_reveal("mutate_1", title = "## mutate_at")`

```{r mutate_1, include = FALSE}
library(tidyverse)
set.seed(215)

# 1 to 7 rating; 99 = missing
values <- c(1:7, 99)

# example data frame 
dat <- tibble(
  "A_1" = sample(values, 10, TRUE),
  "A_2" = sample(values, 10, TRUE)
  )

# re-code 99 to missing
dat %>%
  mutate_at(
    vars(matches("A")),
    na_if, 99
    )
```


---

`r chunk_reveal("mutate_2", title = "## mutate_at, cont.")`

```{r mutate_2, include = FALSE}
# create new variables with re-coded values
dat %>%
  mutate_at(
    vars(matches("A")), 
    list(clean = ~ na_if(., 99))
    )
```

---

`r chunk_reveal("mutate_3", title = "## mutate_at, cont.")`


```{r mutate_3, include = FALSE}
# multiple steps to track a 
# data cleaning process
# a top 2 box is a 6 or 7 
# on a 1-7 rating scale
dat %>%
  mutate_at(
    vars(matches("A")), 
    list(clean = ~ na_if(., 99))
    ) %>%
  mutate_at(
    vars(matches("clean")), 
    list(
      box = ~ case_when(
        is.na(.)   ~ NA_character_,
        . %in% 6:7 ~ "top 2",
        . %in% 1:5 ~ "other")
  ))
```


---
class: inverse, middle, center

# 3. mutate + across + matches

<!-- get a flipbook version of the my_cars code chunk - pauses are where parentheses are balanced -->

---

`r chunk_reveal("mutate_across_1", title = "## mutate + across")`

```{r mutate_across_1, include = FALSE}
library(tidyverse)
set.seed(215)

# 1 to 7 rating; 99 = missing
values <- c(1:7, 99)

# example data frame 
dat <- tibble(
  "A_1" = sample(values, 10, TRUE),
  "A_2" = sample(values, 10, TRUE)
  )

# re-code 99 to missing
dat %>%
  mutate(
    across(matches("A"),
      na_if, 99
    ))
```


---

`r chunk_reveal("mutate_across_2", title = "## mutate + across, cont.")`

```{r mutate_across_2, include = FALSE}
# create new variables with re-coded values
dat %>%
  mutate(
    across(matches("A"), 
    list(clean = ~ na_if(., 99))
    ))
```

---

`r chunk_reveal("mutate_across_3", title = "## mutate + across, cont.")`


```{r mutate_across_3, include = FALSE}
# multiple steps to track a 
# data cleaning process
# a top 2 box is a 6 or 7 
# on a 1-7 rating scale
dat %>%
  mutate(
    across(matches("A"), 
    list(clean = ~ na_if(., 99))
    )) %>%
  mutate(
    across(matches("clean"), 
    list(
      box = ~ case_when(
        is.na(.)   ~ NA_character_,
        . %in% 6:7 ~ "top 2",
        . %in% 1:5 ~ "other")
  )))
```


---
class: inverse, middle, center

# 4. haven + gtsummary

<!-- get a flipbook version of the my_cars code chunk - pauses are where parentheses are balanced -->

---

`r chunk_reveal("haven_gt", title = "## {haven} + {gtsummary}")`

```{r haven_gt, include = FALSE}
library(tidyverse)
library(here)
library(haven)
library(gtsummary)

dat <- haven::read_sav(
  here("data", "sadc_2017_national.sav")
  )

dat %>% 
  count(q8) 
```

---

`r chunk_reveal("haven_gt2", title = "## {haven} + {gtsummary}")`


```{r haven_gt2, include = FALSE}
dat %>% 
  dplyr::select(q8) %>% 
  mutate(q8 = haven::as_factor(q8)) %>% 
  tbl_summary()
```




---
class: inverse, middle, center

# 5. `scales::show_col(_)`

---

`r chunk_reveal("show-col", title = "## scales::show_col")`


```{r show-col, include = FALSE}
rladies_colors <- c(
  "#181818", 
  "#D3D3D3", 
  "#88398A", 
  "#FFFFFF", 
  "#562457"
  )

scales::show_col(rladies_colors)

```


---
class: inverse, middle, center

# 6. named color vectors

---
`r chunk_reveal("ggplot-col", title = "## Named color vectors +  scale_color_manual")`


```{r ggplot-col, include = FALSE}
# example data 
dat <- tibble(x = 1:8) %>%
  mutate(
    bucket = case_when(
      x %in% 1:2 ~ "A",
      x %in% 3:4 ~ "B",
      x %in% 5:6 ~ "C",
      x %in% 7:8 ~ "D")
    )

dat
```


---

`r chunk_reveal("ggplot-col-2", title = "## Named color vectors +  scale_color_manual")`


```{r ggplot-col-2, include = FALSE}
# named color vector
rladies_colors <- c(
  "A" = "#181818", 
  "B" = "#562457",
  "C" = "#88398A", 
  "D" = "#D3D3D3"
)

dat %>% 
  ggplot(
    aes(x = x, 
        y = x, 
        color = bucket)
    ) +
  geom_point(size = 4) +
  scale_color_manual(
    values = rladies_colors
    ) +
  theme_void()
```

